A Closer Look at Time-Preserving Paths on Evolving Graphs

### 2017-11-04 paper.tex
various updates and fixes

A time-preserving path on evolving graphs makes implicit assumptions about the type of edges in which a path traverse. For example, some papers count only static edges,
while some take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.

We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
We construct an evolving coauthor network from a collection of research papers for the experiments.
\end{abstract}

@@

In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed the history.
However, we cannot travel back in time or even send a message to the past.
An evolving graph in general is a time dependent graph $G(t) = (V(t), E(t))$.
To traverse an evolving graph, one has to consider time. In particular, a path on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.

% time-respecting path
We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{tang10, tang102, tang09, nicosia13} and Grindrod, Higham and coworkers \cite{grindrod11, grindrod13}. The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer. A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of
$G^{[t]}$ and $t$ is the time stamp of the slice. A time-respecting path of length $n$ is a sequence of these node pairs $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$. Note if $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge at a temporal slice,  otherwise it is an edge linking nodes from different temporal slices.
We call edges of the first kind \emph{static edges} and of the second kind
\emph{causal edges}.
For example, in Figure \ref{fig:eg_shortest_path}
$\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
The difference between static edges and causal edges were introduced in \cite{chen16}.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};
  \node[circle,draw=red1, minimum size=0.2cm] (n6) at (3,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {1};

   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n12) at (6,5)  {3};
  \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {1};

  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
 \draw[dotted,->](n4) -- (n12);
\draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows.}
\label{fig:eg_shortest_path}
\end{figure}

@@

% our contribution this paper
Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality. In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only count static edges.
Tang et al. \cite{tang10s} measures a temporal shortest path in time unites (or causal edges) only. If a node can reached by another node in $k$ time stamps then the distance between the two nodes is $k$. Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path.

The aim of this paper is as follows. First, to identity the type of time-preserving path in a list of common evolving graph centrality measures. Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
We design the experiment using the Julia dynamic network analysis package
EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
We use the research paper data gathered from Etymo (\url{https://etymo.io}), a visual search engine for data scientists.

@@

A \textbf{walk} of length $r$ from node $i_1$ to node $j_{r+1}$ is a sequence of edges
$(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.

@@

% definition of various graph centrality algorithms
We review the Katz centrality here.
Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. Suppose $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
\[
(I - \alpha A)^{-1}e.
\]

@@

We now describe time-preserving paths in more details. We follow the definition of
\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.

@@

\begin{definition}
A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots t_m$ and
$v_i = v_j$ if and only if $t_i \ne t_j$.
\end{definition}

@@

A time-preserving path can traverse both causal edges and static edges.
We will see in the next section evolving centrality measures make implicit assumptions about the type of edges in the
time-preserving path that is used.

@@

We can not travel back in time. But reverse the direction of temporal flows can help
identify the ``hub'' nodes or the source of the flows. The authority score of a page is
proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
Indeed, reverse PageRank has
been studied by \cite{fogaras03, bar08, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
Fogaras \cite{fogaras03} shows that Reversed Page Rank sores express hub quality.

@@

If we use this definition of temporal path for the temporal Katz centrality introduced by
\cite{grindrod11}, we have a new centrality measure.
In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
number of walks, i.e., longer walks has smaller effect to the overall rating.
Hence the final result is the summation of all products of the form
\[
\alpha^k A^{[i]} \cdots A^{[i+k]}
\]
Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.

Another definition of temporal path was introduced by \cite{chen16}. Here
both static edges and causal edges are considered. We can represent an evolving graph with a block adjacency matrix. Centraliy on this block matrix gives the importance of each node at all time stamps. We can average these rating at different time stamps to
get the final rating.

@@

In \cite{grindrod11}, Grindrod et al. defines a \emph{dynamic walk} of length $m$ from
node $v_1$ to node $v_{w+1}$  as a sequence of edges
$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$. Note in this definition, the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.

@@

One may want to take into account the length of time a node trains a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
\begin{equation}
  \label{eq:bet2}
  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
\end{equation}
where as before $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
the path in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
average temporal betweenness of node $i$ is then defined as
$$
  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
$$
Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.

@@

Let $d_{ij}$ is the length of temporal shortest path from $i$ and $j$ in an evolving graph. Then
the closeness centrality of a node $i$ is defined
$$
C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
$$
Note depends on how we define the length of temporal shortest path, the closeness centrality can takes account of only static edges, only causal edges, or both.

@@

In \cite{chen16}, we derive a block adjacency matrix representation.
Let $E'$ be the set of causal edges and $\hat E$ be the set of static edges then
an evolving graph can be represented as
$$
\bm M_n =
\begin{pmatrix}
A^{[t_1]} & M^{[t_1, t_2]} & \ldots & M^{[t_1, t_n]} \\
0         & A^{[t_2]} & \ldots & M^{[t_2, t_n]} \\
          & \ldots    &        &     \\
0         & 0         & \ldots & A^{[t_n]}
\end{pmatrix},
$$
where $M^{[t_i, t_j]}$ is the matrix whose rows are labeled by $V^{[t_i]}$ and columns are labeled by $V^{[t_j]}$, and whose entries are
$$
  M_{uv}^{[t_i, t_j]} =
  \begin{cases}
    1 & \mbox{if} (u, v) \in E' \\
    0 & \mbox{otherwise}.
  \end{cases}
$$
The adjacency matrix blocks $A^{[t]}$ encode the static edge set $\hat E$, whereas the off-diagonal blocks $M^{[t_i, t_j]}$ encode the causal edge set $E'$.

We can apply static graph centrality algorithms to $M_n$ and then take the average of ratings at each each time stamp. For example, we can construct the Google matrix
$G_n$ from $M_n$ and the ranking of the nodes can be found by solving
$$
 r= G_n r.
$$

@@

We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) papers from $2001$ to $2017$ with authors involved. We regard each year
as a time stamp and there are $17$ time stamps in total. At each time stamp, we
create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.

>>>>

A time-preserving path on evolving graphs makes implicit assumptions about the type of edges that a path traverses. For example, the path can count only static edges or can take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.

We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
We construct an evolving coauthor network from a collection of research papers for the experiments.
\end{abstract}

@@

In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed history.
However, we cannot travel back in time or even send a message to the past.
An evolving graph in general is a time-dependent graph $G(t) = (V(t), E(t))$.
To traverse an evolving graph, one has to consider time. In particular, a path on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.

% time-respecting path
We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{nicosia13, tang09, tang102, tang10} and Grindrod, Higham and coworkers \cite{grindrod13,grindrod11}. The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer. A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of
$G^{[t]}$ and $t$ is the time stamp of the slice. A time-respecting path of length $n$ is a sequence of these node pairs $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$. Note if $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge at a temporal slice,  otherwise it is an edge linking nodes from different temporal slices.
We call edges of the first kind \emph{static edges} and of the second kind
\emph{causal edges}.
For example, in Figure \ref{fig:eg_shortest_path}
$\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};
  \node[circle,draw=red1, minimum size=0.2cm] (n6) at (3,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {1};
   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n12) at (6,5)  {3};
  \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {1};
  \node (w1) at (-6, 9) {$w_1$};
  \node (w2) at (3, 13) {$w_2$};
  \node (w3) at (-2, 8) {$w_3$};
  \node (w4) at (2, 4) {$w_4$};
  \node (w5) at (8.5, 7) {$w_5$};s
  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
 \draw[dotted,->](n4) -- (n12);
\draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows, where $w_1, w_2 \ldots w_5$ are edge weights.}
\label{fig:eg_shortest_path}
\end{figure}

@@

% our contribution this paper
Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality. In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
Tang et al. \cite{tang10s} measure a temporal shortest path in time unit (or causal edges) only. If a node can be reached by another node in $k$ time stamps then the distance between the two nodes is $k$. Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path.

The aims of this paper are as follows. First, to identify the type of time-preserving path in a list of common evolving graph centrality measures. Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
We carry out the experiment using the Julia dynamic network analysis package
EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
We use the research paper data gathered from Etymo (\url{https://etymo.io}), a visual search engine for data scientists.

@@

A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
$(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.

@@

% definition of various graph centrality algorithms
We review the Katz centrality here.
Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
\[
(I - \alpha A)^{-1}e.
\]

@@

We now describe time-preserving paths in more detail. We follow the definition of
\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.

@@

\begin{definition}
A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
$v_i = v_j$ if and only if $t_i \ne t_j$.
\end{definition}

@@

A time-preserving path can traverse both causal edges and static edges.
We will see in the next section that evolving centrality measures make implicit assumptions about the type of edges in the
time-preserving path that is used.

@@

We can not travel back in time. But reversing the direction of temporal flows can help
identify the ``hub'' nodes or the source of the flows. The authority score of a page is
proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
Indeed, reverse PageRank has
been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.

@@

If we use this definition of temporal path for the temporal Katz centrality introduced in
\cite{grindrod11}, we have a new centrality measure.
In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
number of walks, i.e., longer walks has smaller effect to the overall rating.
Hence the final result is the summation of all products of the form
\[
\alpha^k A^{[i]} \cdots A^{[i+k]}
\]
% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.

Another definition of temporal path was introduced by \cite{chen16}. Here
both static edges and causal edges are considered. We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}. Centrality on this block matrix gives the importance of each node at all time stamps. We can average these rating at different time stamps to
get the final rating.

@@

In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
node $v_1$ to node $v_{w+1}$  as a sequence of edges
$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$. Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.

@@

One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
\begin{equation}
  \label{eq:bet2}
  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
\end{equation}
where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
the path in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
average temporal betweenness of node $i$ is then defined as
$$
  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
$$
Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.

@@

Let $d_{ij}$ be the length of a temporal shortest path from $i$ and $j$ in an evolving graph. Then
the closeness centrality of a node $i$ is defined
$$
C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
$$
Note that this depends on how we define the length of temporal shortest path. The closeness centrality can takes account of only static edges, only causal edges, or both.

@@

In \cite{chen16}, we derive a block adjacency matrix representation of an evolvign graph.
If $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
an evolving graph can be represented as
$$
\bm M_n =
\begin{pmatrix}
A^{[t_1]} & M^{[t_1, t_2]} & \ldots & M^{[t_1, t_n]} \\
0         & A^{[t_2]} & \ldots & M^{[t_2, t_n]} \\
          & \ldots    &        &     \\
0         & 0         & \ldots & A^{[t_n]}
\end{pmatrix},
$$
where $M^{[t_i, t_j]}$ is the matrix whose rows are labeled by $V^{[t_i]}$ and columns are labeled by $V^{[t_j]}$, and whose entries are
$$
  M_{uv}^{[t_i, t_j]} =
  \begin{cases}
    1 & \mbox{if} (u, v) \in E' \\
    0 & \mbox{otherwise}.
  \end{cases}
$$
The adjacency matrix blocks $A^{[t]}$ encode the static edge set $\hat E$, whereas the off-diagonal blocks $M^{[t_i, t_j]}$ encode the causal edge set $E'$.

(Need to justify the benefit of this approach.)
We can apply static graph centrality algorithms to $M_n$ and then take the average of ratings at each each time stamp. For example, we can construct the Google matrix
$G_n$ from $M_n$ and the ranking of the nodes can be found by solving
$$
 r= G_n r.
$$

@@

We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) from $2001$ to $2017$ with authors involved. We regard each year
as a time stamp and there are $17$ time stamps in total. At each time stamp, we
create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.
(add results here.)
